### 2009-07-08 docs/architecture/architecture.tex
minor fixes

\begin{verbatim}
    do n=1,nlevs

       do i = 1, s(n)%nboxes
\end{verbatim}

@@

       do i = lo(1), hi(1)
          y = prob_lo(2) + (dble(j) + HALF)*dx(2)

@@

The three-dimensional case is similar, with the {\tt density} array
declared as {\tt density(lo(1)-ng\_sp:,lo(2)-ng\_sp:,lo(3)-ng\_sp)},
and an additional loop over the `z' coordinate (from {\tt lo(3)} to
{\tt hi(3)}).

>>>>

\begin{verbatim}
    do n=1,nlevs
       do i = 1, s(n)%nboxes
\end{verbatim}

@@

       do i = lo(1), hi(1)
          x = prob_lo(1) + (dble(i) + HALF)*dx(1)

@@

The three-dimensional case is similar, with the {\tt density} array
declared as 
\begin{verbatim}
  density(lo(1)-ng_sp:,lo(2)-ng_sp:,lo(3)-ng_sp)
\end{verbatim}
and an additional loop over the `z' coordinate (from {\tt lo(3)} to
{\tt hi(3)}).
